\include{shared/ietf-slides.tex}

% about the presentation
\title[Applying GREASE to EDHOC]{Applying Generate Random Extensions And Sustain Extensibility (GREASE) to EDHOC Extensibility}
\subtitle{\texttt{draft-ietf-core-edhoc-grease-03}}
\author{Christian~Amsüss}
\date{LAKE at IETF126 / Vienna, 2026-07-20}

\begin{document}

\frame{\titlepage}

\begin{frame}{GREASE}\Large
  \begin{itemize}
  \color{gray}
    \item ``Only by using the extension capabilities of a protocol is the availability of that capability assured.'' \rfc{9170}
    \item This draft just does that.
  \end{itemize}
\end{frame}

\begin{frame}{Status: WGLC completed, revised version submitted}\Large
  Processed input from
  \begin{itemize}
    \item Marco Tiloca (all addressed)
    \item Meiling Chen (all addressed)
      \begin{itemize}
        \item \Large What if someone hardcodes?
      \end{itemize}
    \item Shujaatali Badami (see next slides)
  \end{itemize}
\end{frame}

\begin{frame}{Responding to Shujaatali's concerns}\Large
  \framesubtitle{Part I: For implementations}
  \begin{itemize}
    \item \rfc{8701} says ``SHOULD NOT retry''
      \begin{itemize}
        \item \Large works for browser but not for interfaceless device
        \item focusing on reporting
        \item \ietfdraft{iab-protocol-greasing} is not strict either
      \end{itemize}
    \bigskip
    \item<2-> How should GREASE related failure be reported?
      \begin{itemize}
        \item \Large Informally pointing to CORECONF now.
        \item Distinct from public reporting (out of scope).
      \end{itemize}
    \bigskip
    \item<3-> Quality of randomness -- point to \rfc{4086} or \rfc{8937}
      \begin{itemize}
        \item \Large informal pointer to using existing cryptographic source
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Responding to Shujaatali's concerns}\Large
  \framesubtitle{Part II: For text and process}
  \begin{itemize}
    \item Racing \ietfdraft{spm-lake-pqsuites} on new column
      \begin{itemize}
        \item \Large Algorithms can be ``used'' with any method.
      \end{itemize}
    \bigskip
    \item Racing with other documents for numbers
      \begin{itemize}
        \item \Large IANA may assign different numbers -- \\ as long as encoding retains its shape.
      \end{itemize}
    \bigskip
    \item Test vectors
      \begin{itemize}
        \item \Large IMO not practical; extension points are part of EDHOC.
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Next steps}\Large
  \begin{itemize}
    \item Shepherd writeup
    \bigskip
    \item Solicited feedback from \ietfdraft{iab-protocol-greasing} authors can be part of IETF consensus call.
      \begin{itemize}
        \item \Large ``add grease when seeing grease'' → \\ ``add grease when seeing unprocessed options''?
        \item s/GREASE/grease/
      \end{itemize}
  \end{itemize}
\end{frame}

\end{document}
