\include{shared/ietf-slides.tex}

% about the presentation
\title[Applying GREASE to EDHOC]{Applying Generate Random Extensions And Sustain Extensibility (GREASE) to EDHOC Extensibility}
\subtitle{\texttt{draft-ietf-core-edhoc-grease-00}}
\author{Christian~Amsüss}
\date{LAKE at IETF122 / Bangkok, 2025-03-18}

\begin{document}

\frame{\titlepage}

\begin{frame}{GREASE}\Large
  \begin{itemize}
    \item ``Only by using the extension capabilities of a protocol is the availability of that capability assured.'' \rfc{9170}\footnote{Also \ietfdraft{edm-protocol-greasing}.}
    \item This draft just does that.
  \end{itemize}
\end{frame}

\begin{frame}{Major question: Are COSE headers a greasable extension point?}\framesubtitle{On the nature of \texttt{ID\_CRED\_x}}\Large
  \texttt{ID\_CRED\_I = \{4: 'one', 12345: "narf"\}}

  \texttt{\{-12345: 99999999(["zort", null, [\{\}]]), 14: \{8: ...\}\}}

  \bigskip

  Outcomes:

  \begin{enumerate}
    \item It's not a usable extension point.
    \item Grease it.
  \end{enumerate}

  \vfill

  {\footnotesize{\url{https://github.com/lake-wg/grease/issues/1}}}
\end{frame}

\begin{frame}{Other questions}\Large
  \begin{itemize}
    \item Open: Be explicit about failure when seeing critical form?

      \bigskip

      Editorial -- mechanics are clear, using it this way is out of scope.

      {\footnotesize{\url{https://github.com/lake-wg/grease/issues/2}}}

      \bigskip

    \item Closing: Only Initiator can grease suites.

      \bigskip

      Yes.

      \bigskip
  \end{itemize}
\end{frame}

\begin{frame}{Interop}\Large
  \begin{enumerate}
    \item Fix own libraries.
    \item Try with others.
  \end{enumerate}
\end{frame}

\begin{frame}{Next steps}\Large
  \begin{itemize}
    \item Answer COSE header question. Need help.
      \bigskip
    \item Interop: Hold at which stage until done?
  \end{itemize}
\end{frame}

\end{document}
