\documentclass[aspectratio=169,colorlinks]{beamer}
\usetheme{Boadilla} % plainest one with slide number footer
% The empty linkcolor is mainly to not have a non-matching color in the presentation name in the footer
\hypersetup{colorlinks,linkcolor=,urlcolor=blue!50!black}

% generic packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{verbatim}

% about the presentation
\title[Applying GREASE to EDHOC]{Applying Generate Random Extensions And Sustain Extensibility (GREASE) to EDHOC Extensibility}
\subtitle{\texttt{ draft-amsuess-core-edhoc-grease}}
\author{Christian~Amsüss}
\date{IETF118 Prague, LAKE, 2023-11-06}

% This should be my "always used in presentations" git module
\newcommand{\rfc}[1]{\href{https://datatracker.ietf.org/doc/html/rfc#1}{RFC~#1}}
\newcommand{\ietfdraft}[1]{\href{https://datatracker.ietf.org/doc/draft-#1/}{draft #1}}

% for check marks
\usepackage{pifont}
\usepackage{amssymb}

% attach self

\usepackage{embedfile}
\embedfile{\jobname.tex}
\embedfile{Makefile}

\begin{document}

\frame{\titlepage}

\begin{frame}{Long time ago in London\ldots}\Large
    % 2018
  ``EDHOC will start small and then add all things in TLS back in.''

  \bigskip

  Let's be selective -- and then mindfully take good parts (e.\,g. \rfc{8701}).
\end{frame}

\begin{frame}{GREASE}\Large
  \begin{itemize}
    \item EDHOC has extension points
    \item Implementations often just see what they expect
    \item Middleboxes can often just deal with what they expect
  \end{itemize}

  \bigskip

  \ldots so if extension points go unused, they might become unusable.

  \bigskip

  We apply GREASE to prevent the joins from rusting shut.
\end{frame}

\begin{frame}{Concrete extension points}\Large
  \begin{itemize}
    \item[\ding{52}] EAD items: $1\times$ 1+1, $3\times$ 1+2; all optional
    \item[\ding{52}] Cipher suites: $1\times$ 1+1, $3\times$ 1+2; responder can't select them
    \item[?] Methods: Not negotiated
    \item[?] COSE headers: Not negotiated % someone more versed in COSE might know a way how we could extend this still, and not fail with a GREASE unaware peer (which is a tacit base requirement).
  \end{itemize}

  \bigskip

  \ldots and if we could do the latter, should we?
\end{frame}

\begin{frame}{Caveats}\Large
  \begin{itemize}
    \item We're message size constrained.

      $\to$ Apply it in applications where the added size will be tolerable.

    \item It can be a covert channel (cf. INTDIR on padding).

      $\to$ Yes. As can the use of any other EAD.

    \item The distribution and values of options reveal some data about the implementation.

      $\to$ Concrete recommendation available on size and choice -- \\large anonymity set.
  \end{itemize}
\end{frame}

\begin{frame}{Advancing GREASE for EDHOC}\Large
  \begin{itemize}
    \item Check against \rfc{9170} guidance.
    \item Check against \ietfdraft{edm-protocol-greasing} and \href{https://datatracker.ietf.org/meeting/118/session/edm}{upcoming work}.
    \item Fit in the WG?
    \item Should be an easy document.
  \end{itemize}
\end{frame}

\end{document}
