\include{shared/ietf-slides.tex}

% about the presentation
\title[Applying GREASE to EDHOC]{Applying Generate Random Extensions And Sustain Extensibility (GREASE) to EDHOC Extensibility}
\subtitle{\texttt{ draft-amsuess-core-edhoc-grease}}
\author{Christian~Amsüss}
\date{IETF121 Dublin, LAKE, 2024-11-04}

\begin{document}

\frame{\titlepage}

\begin{frame}{Long time ago in London\ldots}\Large
    % 2018
  ``EDHOC will start small and then add all things in TLS back in.''

  \bigskip

  Let's be selective -- and then mindfully take good parts (e.\,g. \rfc{8701}).
\end{frame}

\begin{frame}{GREASE}\Large
  \begin{itemize}
    \item ``Only by using the extension capabilities of a protocol is the availability of that capability assured.'' \rfc{9170}\footnote{Also \ietfdraft{edm-protocol-greasing}.}
    \item This draft just does that.
  \end{itemize}
\end{frame}

\begin{frame}{Concrete extension points}\Large
  \begin{itemize}
    \item[\ding{52}] EAD items: 1$\times$ ``1+1'', 3$\times$ ``1+2''; all optional
    \item[\ding{52}] Cipher suites: 1$\times$ ``1+1'', 3$\times$ ``1+2''; responder can't select them
    \item[\ding{54}] Methods: Not negotiated -- out of scope
    \item[\ding{54}] COSE headers: Not negotiated -- out of scope % someone more versed in COSE might know a way how we could extend this still, and not fail with a GREASE unaware peer (which is a tacit base requirement).
  \end{itemize}

  \bigskip

  \ldots exercising the extension points we \textit{can} keep utilized.
\end{frame}

\begin{frame}{Advancing GREASE for EDHOC}\Large
  \begin{itemize}
    \item All is done that can be done in an individual draft.
  \end{itemize}

  \vspace{2cm}
  \pause

  \raggedleft Chairs?
\end{frame}

\begin{frame}{Backup slide: Caveats}\Large
  \begin{itemize}
    \item We're message size constrained.

      $\to$ Apply it in applications where the added size will be tolerable.

    \item It can be a covert channel (cf. INTDIR on padding).

      $\to$ Yes. As can the use of any other EAD.

    \item The distribution and values of options reveal some data about the implementation.

      $\to$ Concrete recommendation available on size and choice -- \\large anonymity set.
  \end{itemize}
\end{frame}

\end{document}
